### 2018-01-03 icde/revision/Response.tex

\textbf{[R2D3]} \emph{On page 4, you say ``However, the resulting author citation graph to compute the prestige is typically too large to handle". This is a questionable statement. Maybe it is too large to handle ``on a PC with 2 Intel Xeon E5¨C2630 2.4GHz CPUs and 64 GB of memory" but approaches like PageRank has been used for web-scale data so unless there is something that I am missing, this statement should also go (or explained better).}

We agree that this sentence does not make sense, and, hence, we have removed the sentence, and explained more details about the statement (Author Component, left column, page 4). Thanks!

Yes, distributed processing is adopted for PangRank computation at Google, and we plan to develop a distributed version of our algorithm as well.
However, even this, memory cost should also be deliberately considered in a centralized case.

One way to compute the prestige of authors is to construct an author citation graph  such that (1) a node represents an author, and (2) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$. However, it is easy to see that for each citation, the corresponding two sets of authors are fully connected, which makes it computationally expensive to compute the prestige of authors on such an author citation graph with TWPageRank.

@@

\textbf{[R3D1]} \emph{Although the authors have a detailed introduction about the growing data, detailed figures about the data are recommended in the introduction.}

Yes, we  have added the volume statistics (the number of articles published at each year) of the growing data in Figure 1. Thanks!

\textbf{[R3D3]} \emph{It is suggested that the authors should include some references to papers addressing the time delaying problem such as temporal graph, since it is related to the topic.}

Yes, we have discussed the correlation between our work and temporal graphs, and cited necessary references (e.g., P. Holme and J. Saramaki, ¡°Temporal networks,¡± Physics Reports, vol. 519, no. 3, pp. 97 ¨C 125, 2012) in related work (Section VI).

### 2018-01-03 icde/revision/Response.tex

\textbf{[R2W2]} \emph{Presentation could improve a bit since the paper has too much notation making it hard to read/follow.}

Yes, we have gone over the paper, and tried our best to improve its presentation.
%Thanks for the suggestion!

\textbf{[R2D2]} \emph{The abstract starts with the sentence ``Ranking query independent scholarly articles is a critical and challenging task, due to the heterogeneous, evolving and dynamic nature of entities involved in scholarly articles". If three types of data (articles, authors and venues) that are updated (maybe) weekly is considered challenging in terms of heterogeneity and dynamicity then one must wonder what one can say about real-life scenarios with thousands of data types where hundreds/thousands of new items are inserted daily (consider any online merchant system) and were ranking is important (recommendations). In summary, this sentence should go. Not to mention that the task is not really ``critical".}

We have downgraded the tone to ``a practical and difficult problem''. Thanks for the suggestion!

@@

\textbf{[R2D3]} \emph{On page 4, you say ``However, the resulting author citation graph to compute the prestige is typically too large to handle". This is a questionable statement. Maybe it is too large to handle ``on a PC with 2 Intel Xeon E5¨C2630 2.4GHz CPUs and 64 GB of memory" but approaches like PageRank has been used for web-scale data so unless there is something that I am missing, this statement should also go (or explained better).}

We agree that this sentence does not make sense, and, hence, we have removed the sentence, and explained more details about the statement (Author Component, left column, page 4). Thanks!

Yes, distributed processing is adopted for PangRank computation at Google, and we plan to develop a distributed version of our algorithm as well.
However, even this, memory cost should also be deliberately considered in the centralized case.

@@

\textbf{[R3W1\&D2]} \emph{More examples are suggested, especially when introducing the definitions, to make it easier for readers to understand.}

Yes, thanks for the nice suggestion! Due to the space limitation, we have added the examples to the full version (https://hurenjun.github.io/SARank-full.pdf).

\textbf{[R3W2\&D4]} \emph{The memory cost of the algorithms is better to be reported in the experiments.}

We have reported the memory cost with a new set of tests in the experimental study (Exp-4, page 9). Thanks for the suggestion!
%that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$. Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms. seperate exp, between two baselines, author citation graph
%the memory cost of (\pagerank, \futurerank, \ensemblerank) is (12.65GB, 16.42GB, 49.42GB) when $Y_s=2015$, and the one of \hhgrank is 61.37GB when $Y_s=2014$.

### 2018-01-03 icde/revision/Response.tex

\textbf{Response to the comments of Referee 2.}

\textbf{[R2W1\&D1]}
\emph{While practically the paper makes a good case about the particular application domain and its contributions there, the paper lacks technical depth.} \\
\emph{There seem to be two ``contradictory" sides to this paper. From one side, this is a great ``applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem. From a purely research and technical perspective, the paper is on the weak side. PageRank and (incremental) versions of it already exist and the paper makes little contributions there. The claim (made twice) in the related work section that ``Different from previous work" this paper focuses on citations statistics doesn't hold water. The fact that the authors are considering a different application domain is not a contribution compared to past (incremental) pagerank papers. Unless there is a better claim to be made about the algorithmic side of the paper, as things stand, the paper makes minimal technical contributions.}

Yes, our work comes from a practical need from industries. We thank the reviewer for appreciating this merit of our work.

We do believe that there are technical contributions: (1) An ensemble based ranking model (a great effort needs to be paid to develop such a ranking model);  (2) An incremental algorithm designed for dynamic scholarly article ranking in the general setting, which is designed for the block-wise algorithm of Time-Weighted PageRank, and is based on the citation characteristics. These have never been exploited in previous studies. That is, we are not simply using known techniques for an application.

More specifically, the only existing dynamic scholarly article ranking solution [21] is based on an impractical assumption that there are no citations between articles of the same years. In this work, we study dynamic scholarly article ranking in the general setting by eliminating the strong and impractical assumption. Our incremental algorithm is designed for the block-wise algorithm of Time-Weighted PageRank, and is based on the citation characteristics (\eg for the maintenance of the topological order), both of which have never been exploited before.

### 2018-01-04 icde/revision/sec-alg.tex

\vspace{-0.5ex}
\stitle{Analysis of algorithm \twprscc}. While similar block-wise algorithms were originally proposed for Web graphs~\cite{Berkhin05}, we next show that they are even better for the TWPageRank computation associated with scholarly data.
%
Given inpute graph $G(V, E)$, the block-wise graph and its topological order can be computed in $O(|V|+|E|)$ time~\cite{CormenLRS01}, and the edges in $E_a$ are only scanned once when updating TWPageRank scores.
From these, we have the following.

>>>>

\vspace{-0.5ex}
\stitle{Analysis of algorithm \twprscc}. While similar block-wise algorithms were originally proposed for Web graphs~\cite{Berkhin05}, we next show that they are even better for the TWPageRank computation associated with scholarly data.
%
%Given inpute graph $G(V, E)$, the block-wise graph and its topological order can be computed in $O(|V|+|E|)$ time~\cite{CormenLRS01}, and the edges in $E_a$ are only scanned once when updating TWPageRank scores.
\markedb{Given inpute graph $G(V, E)$, the block-wise graph and its topological order can be computed in $O(|G|)$ time where $|G|=|V|+|E|$~\cite{CormenLRS01}, and the edges in $E_a$ are only scanned once when updating TWPageRank scores.}
From these, we have the following.

### 2018-01-04 icde/revision/sec-incAlg.tex

Our incremental algorithm \incensemble incrementally computes the popularity and prestige of associate entities.
We consider that an update $\Delta$ = $\Delta V\cup\Delta E$ is added to a (citation or venue) graph $G(V, E)$,
and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citations obey a natural temporal order, \ie an article only cites those published earlier. %, and it is rare for the mutual citations between two articles published in the same time.

@@

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-inc-pop}
Pop_c^+(v) = Pop_c(v) {e^{\sigma (T^+_0-T_0)}} + \sum_{(u,v)\in \Delta E^c} {e^{\sigma (T^+_0-T_u)}},
\end{equation}
\end{small}
%
\noindent where $Pop^+_c(v)$ (resp. $Pop_c(v)$) is the popularity of node $v$ on $G^{c,+}$ (resp. $G^c$), and
$T^+_0$ (resp. $T_0$) is the current time on $G^{c,+}$ (resp. $G^c$).
%
By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time.
%This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.

@@

Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta V|+|\Delta E|)$ time,
(b) updating the TWPageRank scores of nodes in $V_B$ and $V_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, where $t^+$ is  the maximum number of iterations among all \sccs in $G_B$ and $G_C$, and, finally, (c) updating the scores of nodes in $V_A$ costs $O(|V_A|)$ time. From these, the following holds.

@@

Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively, shown in Table~II.
%
(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on the update data only,
%where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
where ($|V|$, $|E|$) are more than (92\%, 89\%) of ($|V^{+}|$, $|E^{+}|$) on all tested citation and venue graphs;
(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total;
(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of total;
Finally, (d) it is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.

>>>>

Our incremental algorithm \incensemble incrementally computes the popularity and prestige of associate entities.
We consider that an update $\Delta$ = $\Delta V\cup\Delta E$ is added to a (citation or venue) graph $G(V, E)$,
and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citations obey a natural temporal order, \ie an article only cites those published earlier, %, and it is rare for the mutual citations between two articles published in the same time.
\markedb{and set $|\Delta |= |\Delta V|+|\Delta E|$.}

@@

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-inc-pop}
Pop_c^+(v) = Pop_c(v) {e^{\sigma (T^+_0-T_0)}} + \sum_{(u,v)\in \Delta E^c} {e^{\sigma (T^+_0-T_u)}},
\end{equation}
\end{small}
%
\noindent where $Pop^+_c(v)$ (resp. $Pop_c(v)$) is the popularity of node $v$ on $G^{c,+}$ (resp. $G^c$), and
$T^+_0$ (resp. $T_0$) is the current time on $G^{c,+}$ (resp. $G^c$).
%
\eat{By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time.}
%This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.
\markedb{By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta G^c|)$ time.}

@@

%Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta V|+|\Delta E|)$ time,
\markedb{Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta G|)$ time,}
(b) updating the TWPageRank scores of nodes in $V_B$ and $V_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, where $t^+$ is  the maximum number of iterations among all \sccs in $G_B$ and $G_C$, and, finally, (c) updating the scores of nodes in $V_A$ costs $O(|V_A|)$ time. From these, the following holds.

@@

Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively, shown in Table~II.
%
%(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on the update data only,
\markedb{(a) It saves $O(|G^c|)$ and $O(|G^v|)$ time when maintaining \sccs and the topological order based on the update data only,}
%where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
where ($|V|$, $|E|$) are more than (92\%, 89\%) of ($|V^{+}|$, $|E^{+}|$) on all tested citation and venue graphs;
(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total;
(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of total;
Finally, (d) it is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.
